Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-06 response.md

We thank the referee for the very thorough analysis and for the detailed suggestions that helped to improve the analysis and the paper overall. In the following, we report the original comment by the referee, followed by our response. 
In the manuscript, we highlighted our changes in boldface.

==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been re-organized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

### 2016-09-06 response.md

We thank the referee for the very thorough analysis and for the detailed suggestions that helped to improve the analysis and the paper overall. In the following, we report the original comment by the referee, followed by our response. 
In the manuscript, we highlighted our changes in boldface.

==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been re-organized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

------------------------------------------
Major Issue II: Statistical Model
------------------------------------------

We used the referee's input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:

### 2016-09-06 response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been re-organized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

------------------------------------------
Major Issue II: Statistical Model
------------------------------------------

We thank the referee for the very thorough analysis of this method and for the detailed suggestions. We used this input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:

We tested a variety of models for fitting f/f_0, including linear, quadratic, cubic, and exponential dependences on redshift; for each of these functional forms, we also tested combinations using either a constant zeta parameter or a zeta function that linearly depends on surface brightness. We compared the relative quality of fits using the Akaike information criteria (AIC); for each case, we found no significant differences in the results based on the choice of model. Full details and code for these tests can be viewed in this Python notebook: https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb.

@@

-----------------------------------
Minor Comment 1
-----------------------------------

***1) Section 3.2: what checking did the authors do to indicate that giving all anonymous classifications a weight of 1 is valid?***

From a strict sense, it is impossible to tell a priori if giving the anonymous classifiers a weight of 1 is valid (since the grouping within the anonymous data is unknown). However, there are large amounts of data from similar projects that support this approach. For the Galaxy Zoo: CANDELS project (Simmons et al. 2016, submitted), which is nearly identical in design to Galaxy Zoo: Hubble and shares a large fraction of the same user base, the distribution of the classifier consistency for both the logged-in and non-logged-in populations peak at the same value (kappa = 0.7). The anonymous users have slightly broader wings, with slightly more addresses at the lowest and highest levels of consistency, but the overall behavior is similar. The roughly 50-50 split between logged-in users and non-logged-in IP addresses is typical of the ratio for Zooniverse crowdsourced projects as a group.

ATTACH: Figure from https://cloud.githubusercontent.com/assets/2357126/17576650/cfc59fbe-5f29-11e6-99b7-c39a43c013b6.png

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Consistency for anonymous users; closes #177
Explain bivariate distributions (MiC 2); closes #178.

Classifications for GZH were weighted only if the classifier was logged
into the site under their username (this was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority
of logged-in classifiers.
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data

@@

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images.  These are simulated images of a set of nearby galaxies as
they would appear observed at a variety of redshifts.  The input images are
from the SDSS \citep{yor00,str02}.  The sample consists of 288~well-resolved galaxies
at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
GZ2 classifications, including identifications of spiral structure,
ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
$r$-band surface brightnesses.  The overall selection spanned the
redshift range of SDSS targets and maximised the number of \hst{} galaxies at
the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
\ferengi{} code was used to produce sets of images corresponding to
observations of these galaxies out to $z_\mathrm{sim}=1.0$ (see
Section~\ref{ssec:ferengi}).  The resulting images were classified in the GZH
interface using the standard classification scheme.

>>>>

Classifications for GZH were weighted only if the classifier was logged
into the site under their username (this was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
logged-in classifiers. Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
show that the distributions of weights for anonymous and
logged-in users are similar, supporting the default technique of GZH. 
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data

@@

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images.  These are simulated images of a set of nearby galaxies as
they would appear observed at a variety of redshifts.  The input images are
from the SDSS \citep{yor00,str02}.  The sample consists of 288~well-resolved
galaxies at $z<0.013$. The galaxies spanned a variety of morphologies (as
selected by GZ2 classifications, including identifications of spiral structure,
ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
$r$-band surface brightnesses.  The selection of galaxies spanned the redshift
range of SDSS targets and maximised the number of \hst{} galaxies at the same
surface brightness and redshift. The \ferengi{} code was used to produce sets
of images corresponding to observations of these galaxies out to
$z_\mathrm{sim}=1.0$ (see Section~\ref{ssec:ferengi}). The resulting images
were classified in the GZH interface using the standard classification scheme.

\changes{Figure~\ref{fig:sb_redshift} shows the distribution in $\mu$ and $z$ of
the artificially-redshifted \textsc{FERENGI} images compared to the genuine
\hst{} images. The full bivariate distributions differ due to a combination of
the detection limits of the \hst{} surveys, intrinsic rareness of bright $\mu$
galaxies in the SDSS volume, and evolution of the stellar populations. Since
the dependence of the debiasing correction is evaluated in separate bins, the
main concern is the existence of an overlap between the two sets of images;
this is the case for almost all of the \hst{} images, which have $\mu >
19$~mag~arcsec$^{-2}$.  The brightest end of the distribution, which has fewer
examples of comparable \textsc{FERENGI} images, correspond to galaxies for
which the debiased correction is expected to be minor.}
